\documentclass[11pt]{article}

\usepackage[a4paper, margin=2.5cm]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
\usepackage{xcolor}

\graphicspath{{figures/}{../reports/figures/}}

\title{A geometry-derived response kernel for the\\
       $B \to K^{*}\mu^{+}\mu^{-}$ angular anomaly:\\
       sign-uniform cross-dataset and cross-channel fit}

\author{%
  Lee Smart\\[2pt]
  \textit{Institute of Vibrational Field Dynamics}\\[2pt]
  \texttt{contact@vibrationalfielddynamics.org}\\[2pt]
  \texttt{@vfd\_org}%
}

\date{April 2026}

\begin{document}

\maketitle

\noindent\textbf{Status:} Preprint, not peer-reviewed.

\noindent\emph{Headline.}
A single fixed response kernel $\kappa(q^{2})$, derived from the
600-cell substrate $V_{600}$ regularised by the golden ratio
$\varphi$ before any contact with LHCb data, provides a consistent
description of the $q^{2}$ behaviour of the
$b\to s\mu^{+}\mu^{-}$ angular anomaly across five independent
datasets covering two collaborations, two isospin partners, and three
decay channels. The kernel \emph{shape} has no
parameters tuned to data; only one dimensionless amplitude $A$ is
fitted per dataset. The fitted amplitude is sign-uniform across all
five fits, and the $B\to K^{*}$ vs $B_{s}\!\to\!\phi$ amplitude ratio
is consistent with the predicted Krüger--Matias basis-correction
factor.

\noindent\emph{Statistical caveat.}
On Akaike model comparison, the kernel and a constant
Wilson-coefficient shift $\mathrm{FREE\_C9}$ (also $k=1$) are
statistically indistinguishable on current data: the per-dataset
$\Delta\mathrm{AIC}$ values span $[-0.24, +1.09]$ around zero, with
stacked Akaike weight $w_{\mathrm{VFD}}=0.35$ vs
$w_{\mathrm{FREE\_C9}}=0.65$. AIC compares per-parameter
goodness-of-fit and does not reward predicting a specific functional
form across datasets; the structural test of whether a fixed
geometry-derived shape can describe heterogeneous datasets is
independent of, and complementary to, the AIC tie. An earlier
linearised analysis (Mode B, linear in $\Delta C_{9}$ via
central-difference slopes) found a marginal preference for the kernel
that does not survive the non-linear refit; the linearised numbers are
retained in \S\ref{sec:method} as a methodology diagnostic only.

\begin{abstract}
We test whether a single fixed response kernel $\kappa(q^{2})$ —
derived from a finite 2I-equivariant graph substrate (the 600-cell
$V_{600}$) regularised by the golden ratio $\varphi$ as a discrete
mass scale, with no shape parameters tuned to data — can describe the
$b\to s\mu^{+}\mu^{-}$ angular anomaly across heterogeneous datasets.
The kernel is the shell-mean projection of the discrete Green's
response $\psi = (L_{V_{600}} + \varphi^{-2} I)^{-1} f$, with $f$ a
uniform source on the equatorial inner-product shell; its continuum
limit is $\kappa(x) = e^{-|x|/\varphi}$ with
$x = (q^{2}-q^{2}_{\mathrm{mid}})/\Delta_{\psi}$, where
$q^{2}_{\mathrm{mid}}$ and $\Delta_{\psi}$ are the
$J/\psi$\,-\,$\psi(2S)$ midpoint and half-spread. Of three discrete
edge-weighting variants, the unweighted Laplacian is selected by a
\emph{pure-geometry criterion} (correlation $0.997$ with the continuum
kernel) decided independently of any LHCb input
(\S\ref{sec:derivation}).

Using \texttt{flavio}~\citep{Straub2018Flavio} for SM and
non-linear-in-$C_{9}$ predictions on each dataset's own bin grid, and
fitting one dimensionless amplitude $A$ per dataset (the only
parameter that touches the data), we report:

\noindent\emph{(i) Universality.}
The same fixed kernel shape describes all five datasets —
LHCb~2015~\citep{LHCb2015BKstmumu},
LHCb~2021 ($B^{+}\!\to\!K^{*+}$)~\citep{LHCb2021BKstpmumu},
CMS~2025~\citep{CMS2025BKstmumu},
LHCb~2025~\citep{LHCb2025BKstmumuComp}, and
$B_{s}\!\to\!\phi\mu\mu$~(LHCb~2015)~\citep{LHCb2015Bsphimumu} — with
one amplitude per dataset and no shape retuning across datasets,
channels, or isospin partners.

\noindent\emph{(ii) Sign uniformity.}
The fitted amplitude is positive in $5/5$ fits, giving an effective
$\Delta C_{9}^{\mathrm{eff}}<0$ in every fit. The kernel reproduces
the established direction of the anomaly across all five independent
measurements; this property would also follow from any centre-peaked
one-parameter shape consistent with the anomaly, but is a non-trivial
check that the kernel does not invert sign on any individual dataset.

\noindent\emph{(iii) Cross-channel ratio.}
The $B\to K^{*}$ ($P$-basis) and $B_{s}\!\to\!\phi$ ($S$-basis)
fitted amplitudes differ by a factor consistent with the Krüger--Matias
basis-correction factor $\sim 2.2$, with a residual $\sim 50\,\%$
overshoot of the basis-corrected prediction that the published
2015 $B_{s}\!\to\!\phi$ statistics cannot currently resolve.

\noindent\emph{(iv) AIC comparison.}
On Akaike model comparison versus a constant $\Delta C_{9}$ shift
$\mathrm{FREE\_C9}$ (also $k=1$), the per-dataset $\Delta\mathrm{AIC}$
values span $[-0.24, +1.09]$ around zero ($2/5$ datasets favour the
kernel, $3/5$ favour the constant shift); the stacked Akaike weight
is $w_{\mathrm{VFD}}=0.35$ vs $w_{\mathrm{FREE\_C9}}=0.65$. On current
data the two models are statistically indistinguishable on AIC.

The kernel describes the $q^{2}$ shape of the anomaly with a fixed,
geometry-derived form across heterogeneous datasets — a structural
claim independent of the AIC tie. AIC measures per-parameter
goodness-of-fit and does not reward making a correct shape prediction
across independent measurements. We do not claim the kernel is the
unique $q^{2}$ shape consistent with the anomaly: a free-width
Gaussian charm-loop proxy fits marginally better in $\chi^{2}$ at the
cost of one extra shape parameter, and whether the kernel is
statistically preferred over a constant Wilson-coefficient shift is a
question current data cannot resolve and will require future
$b\to s\ell\ell$ data. An earlier linearised analysis (linear in
$\Delta C_{9}$ via central-difference slopes) gave a stronger
numerical preference for the kernel that does not survive the
non-linear refit; the linearised numbers are retained in
\S\ref{sec:method} as a linearisation diagnostic only.
\end{abstract}

% =====================================================================
\input{sections/01_introduction.tex}
\input{sections/02_method.tex}
\input{sections/03_derivation.tex}
\input{sections/04_results.tex}
\input{sections/05_stress_tests.tex}
\input{sections/06_cross_dataset.tex}
\input{sections/07_cross_channel.tex}
\input{sections/08_discussion.tex}
\input{sections/09_limitations.tex}
\input{sections/10_conclusion.tex}
% =====================================================================

\section*{Acknowledgements}
We thank the LHCb and CMS collaborations for releasing the
HEPData supplementary tables that made this analysis possible. The
non-linear refit headline of this paper rests entirely on
\texttt{flavio}~\citep{Straub2018Flavio} and
\texttt{wilson}~\citep{Aebischer2018Wilson}; we thank Straub, Aebischer,
and the wider \texttt{flavio} community for maintaining and
documenting these tools, without which this work could not have been
done. The BSZ form-factor
parameterisation~\citep{Bharucha2016BSZ} underlies all SM
predictions. All code and processed data are released under MIT
licence at the project repository~\citep{vfdBAnomalyRepo}.

\section*{Reproducibility}
The complete pipeline (data download, SM table regeneration via flavio,
all WO drivers, figure regeneration, this paper) is reproducible from
the project repository~\citep{vfdBAnomalyRepo} via the included
\texttt{repro/run\_all.sh} script. Persistent caches under
\texttt{data/processed/flavio\_cache.json} avoid re-querying flavio
on subsequent runs.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
